Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-07-12 draft/draft.tex
progress

@@

The following experiments are carried on.
\begin{enumerate}
\item 
Compute ratings and rankings from the full weighted networks.

\item 
Compute ratings and rankings from sparsified versiond of the weighted networks, by randomly removing a varying fraction of links.

\item 
Compute ratings and rankings from sparsified versiond of the weighted networks, by removing a varying fraction of links sorted in decreasing order of absolute weight.
\end{enumerate}

>>>>

\section{
Data
\label{sec:data}
}

The data comprehends 5 soccer leagues from England, France, Germany, Italy and Spain.
Each has 20 teams, with the exception of Germany which has 18.
Each pair of teams of each league plays two games, one as local and another the visitor.
For each game between two teams $i$ and $j$ of a given league, a score $\phi_{ij}\in \RR$ is provided.

Each matrix $\phi$ of scores $\phi_{ij}$ defines a fully connected undirected network for the teams in a league.
In some experiments, some fraction of links is removed from the network according to some criterium, defining a graph $\mathcal{G}$ that is not fully connected.
The graph is promoted to a simplicial complex of 0-simplices, 1-simplices and 2-simplices composed by the nodes, the links and the triplets of connected nodes in $\mathcal{G}$, respectively.
A triplet $ijk$ of the nodes $i$, $j$ and $k$ of $\mathcal{G}$ is connected if the links $ij$, $ik$ and $jk$ belong to $\mathcal{G}$.

From a score $\phi$, a corresponding cochain $f\in C_1^*$ of coordinates $f_{ij}=\phi_{ji}-\phi_{ij}$ is defined.
Also, the cochain $f'\in C_1^*$ of coordinates $f'_{ij}=\phi_j-\phi_i$ with team strengths $\phi_i=\sum_j \phi_{ij}$ is considered.

@@

The following experiments are carried on.
\begin{enumerate}
\item 
Compute ratings and rankings from the full weighted network of scores $\phi_{ij}$.

\item 
Compute ratings and rankings from sparsified versiond of the weighted networks of schores $\phi_{ij}$, by randomly removing a varying fraction of links.

\item 
Compute ratings and rankings from sparsified versiond of the weighted networks, by removing a varying fraction of the weighted links of the weighted matrix of scores $\phi_{ij}$ sorted in decreasing order of absolute weight.

\item 
Compute ratings defining the $f_{ij}=\phi_j-\phi_i$ where the strength $\phi_i = \sum_j w_{ij}$ defines a local potential for the $i$-th team.
\end{enumerate}
